\huge A Better (One-Line!) Title Here

### 2016-10-20 pets2017-paper/pets2017-paper.tex
switch order of setup and recruitment section in second user study section.

{\color {red} 
\subsection{Setup}
We ran our experiment at <redacted>.
%Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of California, Berkeley. 
<redacted> %Xlab 
has 36 Windows~7 laptops, separated by cubicle walls. 
Though Tor Browser runs on other operating systems,
testing was only done on Windows, as a byproduct of using <redacted>. %Xlab.

We augmented the interfaces with instrumentation 
to log every meaningful interaction
(button presses, menu selections, screen changes).
We wrote scripts to automatically set up the simulated censorship environment, install necessary software, 
start the video recording, and save the logs and videos.
We recorded the participants' computer screens
throughout the experiment to capture non-interface activity such as 
web searching and inspection of system networking settings.

\subsection{Recruitment}
We recruited 124 participants, about 20 for each
condition. We recruited half of our users from Craigslist, and half of our participants from 
the <redacted> %Xlab 
participant pool. Although <redacted> %Xlab 
participants are not limited to <redacted> %UC Berkeley 
students and staff,
a majority of the participants are from campus. For this reason, we chose to recruit 
half of our participants from Craigslist to ensure a diverse set of participants. 
The recruitment text vaguely suggests testing a piece of software, and does not require
that users provide information in advance (Appendix~\ref{quantitative-recruitment}). 
Out of our 124 participants, 59 were recruited from the <redacted> %Xlab 
pool and the other 65 were
recruited from Craigslist. Ages ranged from 18 to~68 years
($\mu = 28.9$, $\sigma = 12$). 56.8\% were male and 
84.8\% of our participants had at least a college education.

\subsection{Procedure}
The one-hour, multi-participant procedure began when all participants sat at their
respective computers in <redacted>. %Xlab. 
Each computer was equipped with an instrumented old or new version
of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording).
Each computer was assigned one of the six conditions in the beginning of the study. Participants
were assigned to a simulated censorship environment combination at random.

>>>>

\subsection{Recruitment}
We recruited 124 participants, about 20 for each
condition. We recruited half of our users from Craigslist, and half of our participants from 
the <redacted> %Xlab 
participant pool. Although <redacted> %Xlab 
participants are not limited to <redacted> %UC Berkeley 
students and staff,
a majority of the participants are from campus. For this reason, we chose to recruit 
half of our participants from Craigslist to ensure a diverse set of participants. 
The recruitment text vaguely suggests testing a piece of software, and does not require
that users provide information in advance (Appendix~\ref{quantitative-recruitment}). 
Out of our 124 participants, 59 were recruited from the <redacted> %Xlab 
pool and the other 65 were
recruited from Craigslist. Ages ranged from 18 to~68 years
($\mu = 28.9$, $\sigma = 12$). 56.8\% were male and 
84.8\% of our participants had at least a college education.
}

\subsection{Setup}
{\color {red} 
We ran our experiment at <redacted>.
%Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of California, Berkeley. 
<redacted> %Xlab 
has 36 Windows~7 laptops, separated by cubicle walls. 
Though Tor Browser runs on other operating systems,
testing was only done on Windows, as a byproduct of using <redacted>. %Xlab.

We augmented the interfaces with instrumentation 
to log every meaningful interaction
(button presses, menu selections, screen changes).
We wrote scripts to automatically set up the simulated censorship environment, install necessary software, 
start the video recording, and save the logs and videos.
We recorded the participants' computer screens
throughout the experiment to capture non-interface activity such as 
web searching and inspection of system networking settings.
}
\subsection{Procedure}
{\color {red} 
The one-hour, multi-participant procedure began when all participants sat at their
respective computers in <redacted>. %Xlab. 
Each computer was equipped with an instrumented old or new version
of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording).
Each computer was assigned one of the six conditions in the beginning of the study. Participants
were assigned to a simulated censorship environment combination at random.
